Evaluating FAIR Digital Object and Linked Data as distributed object systems

### 2023-06-26 latex/main.tex
footnotes

From this mapping we can identify the conceptual similarities between DOIP and HTTP, often with common terminology. Notable are that neither DOIP or HTTP have strong support for transactions (explored further \vpageref{sec:middleware}), as well that HTTP has poor direct support for processes, as the Web is primarily stateless by design.

>>>>

From this mapping\footnote{An equivalent SKOS mapping \autocite{w3-skos-primer} is provided as part of the \href{https://w3id.org/ro/doi/10.5281/zenodo.8075229}{RO-Crate for this article} \autocite{stian_soiland_reyes_2023_8075230}.} we can identify the conceptual similarities between DOIP and HTTP, often with common terminology. Notable are that neither DOIP or HTTP have strong support for transactions (explored further \vpageref{sec:middleware}), as well that HTTP has poor direct support for processes, as the Web is primarily stateless by design.
